cd
---
title: "Assignment 2"
output:
  html_document:
    df_print: paged
---
### Load the library





Install the `rvest` package if it is not yet installed
```{r}
if (!("rvest" %in% installed.packages())) {
  install.packages("rvest")
}
library(rvest)
```

### Get the csv example

Load in the html
```{r}
csv_wiki <- read_html("https://en.wikipedia.org/wiki/Comma-separated_values")
```

```{r}
print(csv_wiki)
```





```{r}
library(httr)
library(XML)

url <- "https://en.wikipedia.org/wiki/Comma-separated_values"

r <- GET(url)

doc <- readHTMLTable(
  doc=content(r, "text"))

table <-doc[6]

df =data.frame(table)

colnames(df) = df[1,]

df = df[-1,]

df
```


Get the csv examples under the header "Example"

```{r}
csv_tables <- csv_wiki %>% html_nodes(xpath = '//h2[contains(., "Example")]//following-sibling::pre') %>% html_text()

```

Have a look of the tables:
```{r}
csv_tables[1]
```

The first table is what we want.
```{r}
csv_table <- csv_tables[1]
```

### Save the csv example into a csv file
```{r}
write.table(csv_table, file = "car.csv", quote = FALSE, col.names = FALSE, row.names = FALSE)
```

Reload the csv data from the file to make sure the data was saved properly
```{r}
data <- read.csv("car.csv")
data[1:2,]
```



```{r}
typeof(data$Year)
mean(data$Price)
```

```{r}
summary(data)
```

```{r}
table(data$Year)
```


```{r}
dim(data)
head(data, 2)


```


```{r}

## maximum price of the cars
max(data$Price)


## which car maximum price of the cars
data[which.max(data$Price), 'Make' ]
```


```{r}
boxplot(data$Price)

plot(data$Year, data$Price)



```

